Leveraged Volume Sampling - Summary

### 2019-03-02 summary/paper-summary.tex
finished the lev. vol sampling section

>>>>

        This algorithm runs, with probability at least $1-\delta$, in time $\mathcal{O}((d^2+k^2)d^2ln(\frac{1}{\delta}))$.
        This can be seen by bounding from below the acceptance probability in the repetition with $\frac{3}{4}$ and noting that determinant
        calculation takes at most as much as decomposing a matrix via SVD which is $\mathcal{O}(sd^2)$.
        Finally, note that $s=\mathcal{O}(k+d^2)$.
